Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-09 demystify.tex
updates

@@

\begin{commentbox}[Vu:] 
    I enjoy working with undergrads and have advised many (10+).
    I often recruit undergraduate researchers through my classes, e.g., asking students who did well in my class if they are interested in research.  Occasionally I was introduced to students by other students or faculty.

>>>>

There might be also special programs for undergraduate research from the university, e.g., GMU has the OSCAR program, UNL has UCARE, NSF has REUs (Research Experience for Undergraduates) for US citizen and permanent residents.

@@

\begin{commentbox}[Vu:] 
    I enjoy working with undergrads (e.g., have mentored over 10 undergrads) and actively recruit them.
    I often recruit undergraduate researchers through my classes, e.g., asking students who did well in my class if they are interested in research.  Occasionally I was introduced to students by other students or faculty.
